---
format: 
  gfm:
    embed-resources: false
editor:
    render-on-save: true
execute: 
  echo: false
  warning: false
  fig-width: 10
  fig-height: 5
---


```{r}
library(tidyverse)
library(glue)
library(ggthemes)
library(scales)
```

# Risk Strategies Simulation

Interactive visualizations exploring risk management strategies and their long-term implications, inspired by [Luca Dellanna's work](https://luca-dellanna.com/posts/long-term-risks) on risk management and long-term decision-making.

## Overview

This project provides visual simulations that demonstrate key concepts from risk management research, including ergodicity, survival strategies, and the importance of avoiding catastrophic losses in long-term investment approaches.

## Visualizations

The project includes interactive simulations that demonstrate:

1. **Monte Carlo Risk Simulations**: Comparing different risk strategies over thousands of scenarios
2. **Long-term Performance Analysis**: Time series showing how different strategies perform over extended periods
3. **Risk-Return Trade-offs**: Interactive exploration of the relationship between risk tolerance and long-term outcomes


```{r}
num <- 125000
num_years <- 25
set.seed(44)

data_file <- "data/simulations.csv"

if (file.exists(data_file)) {
    data <- read_csv(data_file)
} else {
    data <- tibble(growth = rnorm(num, 1.15, 0.45)) |>
        mutate(name = "Alice") |>
        mutate(simulation = ceiling(row_number() / num_years)) |>
        bind_rows(
            tibble(growth = rnorm(num, 1.04, 0.12)) |>
                mutate(name = "Bob") |>
                mutate(simulation = ceiling(row_number() / num_years))
        ) |>
        write_csv(data_file)
}


final_capital <- data |>
    group_by(name, simulation) |>
    summarise(total_growth = prod(growth)) |>
    ungroup()
```

```{r parameters}
data |>
    group_by(name) |>
    summarise(mean = mean(growth), sd = sd(growth)) |>
    pivot_longer(cols = c(mean, sd), names_to = "metric", values_to = "value") |>
    ggplot(aes(x = name, y = value, fill = name)) +
    geom_col() +
    facet_wrap(~metric) +
    scale_fill_tableau() +
    theme_minimal() +
    labs(
        title = "Growth Parameters by Strategy",
        subtitle = "Mean and Standard Deviation",
        x = "", y = "Value", fill = "Strategy"
    )
```

```{r wealth_distribution}
final_capital |>
    ggplot(aes(total_growth, fill = name)) +
    geom_histogram(bins = 100) +
    geom_vline(xintercept = 1, linetype = "dotted") +
    scale_x_continuous(trans = "log10", labels = percent) +
    scale_y_continuous(trans = "log10") +
    scale_fill_tableau() +
    facet_wrap(~name) +
    theme_minimal() +
    labs(title = "Alice vs Bob", subtitle = "Wealth Distribution", x = "Total Growth after {num_years} years" |> glue(), y = "Number")
```



```{r ruin_ratio}
final_capital |>
    mutate(ruined = ifelse(total_growth < 1, T, F)) |>
    group_by(name, ruined) |>
    summarise(n = n()) |>
    mutate(ratio = n / sum(n)) |>
    ggplot(aes(x = name, y = ratio, fill = ruined)) +
    geom_bar(stat = "identity") +
    geom_text(
        aes(label = scales::percent(ratio, accuracy = 0.1), group = ruined),
        position = position_stack(vjust = 0.5),
        color = "white",
        size = 4
    ) +
    scale_fill_manual(
        labels = c("FALSE" = "Success", "TRUE" = "Ruined"),
        values = c("FALSE" = "#2ca02c", "TRUE" = "#d62728")
    ) +
    coord_flip() +
    theme_minimal() +
    theme(
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank(),
    ) +
    labs(title = "Alice vs Bob", subtitle = "Success Ratio", x = "", y = "", fill = "")
```


#### Interested in Dev, AI, Modeling, Uncertainty, Decision Support Tools, or Sports Analytics?

This demo was created by Jens Laufer from [Solytics GmbH](https://www.solytics.de) — a team passionate about empowering better decisions under uncertainty.

We specialize in:

- Custom analytics and simulation tools  
- Forecasting, risk modeling, and decision intelligence  
- Data-driven product development  
- Sport Data Analytics
- Fullstack Softwaredevelopment

👉 [Visit solytics.de](https://www.solytics.de) — we’d love to hear from you.
